**Machine learning identifies unique taxa differentiating proximal and distal

### 2017-06-14 submission/manuscript.Rmd
working code into rmd

```{r dependencies}
#setwd('~/Documents/Flynn_LRColon_XXXX_2017')
pack_used <- c('randomForest','ggplot2', 'pROC', 'knitr','dplyr','AUCRF', 'tidyr', 'caret', 'RColorBrewer', 'reshape2', 'wesanderson')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

```{r datasets}
#setwd("~/Users/kaitlinflynn/Documents/Flynn_LRColon_XXXX_2017")
meta <- '../data/raw/kws_metadata.tsv'
shared <- '../data/mothur/kws_final.an.shared'
tax <- '../data/mothur/kws_final.an.cons.taxonomy'
subsample <- '../data/mothur/kws_final.an.0.03.subsample.shared'

@@

>>>>

```{r dependencies}
pack_used <- c('randomForest','ggplot2', 'pROC', 'knitr','dplyr','AUCRF', 'tidyr', 'caret', 'RColorBrewer', 'reshape2', 'wesanderson')
for (dep in pack_used){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), repos = 'http://cran.us.r-project.org', 
                     quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
```

```{r datasets}
meta <- '../data/raw/kws_metadata.tsv'
shared <- '../data/mothur/kws_final.an.shared'
tax <- '../data/mothur/kws_final.an.cons.taxonomy'
subsample <- '../data/mothur/kws_final.an.0.03.subsample.shared'

@@

```{r thetayc}
tyc <- read.table("../data/mothur/kws_final.an.summary", sep = '\t', header = T, row.names=NULL)

#separate column values for comparisons
tyc <- separate(tyc, label, into= c('pt1', 'samp1'), sep="-", remove=F)
tyc <- separate(tyc, comparison, into= c('pt2', 'samp2'), sep="-", remove=F)
tyc <- subset(tyc, select = -c(row.names, X))

tyc <- subset(tyc, pt1==pt2)
tyc <- unite_(tyc, "match", from=c('samp1', 'samp2'), sep="_", remove = F)

stooltyc <- subset(tyc, match=='LB_RB' | match== 'LS_RS')
leftandrighttyc <- subset(tyc, match=='LB_LS' | match== 'RB_RS')
lvsr <- rbind(stooltyc, leftandrighttyc)

exittyc <- subset(tyc, samp2 == 'SS')

pvalues <- c()

Atyc <- subset(tyc, match=='RB_RS' | match=='LS_RS')
pvalues <- c(pvalues, wilcox.test(thetayc~match, data=Atyc, paired=T)$p.value)

btyc <- subset(tyc, match=='RB_RS'| match=='LB_RB')
btyc <- btyc[-25,]
pvalues <- c(pvalues, wilcox.test(thetayc~match, data=btyc, paired=T)$p.value)

ctyc <- subset(tyc, match=='RB_RS'| match=='LB_LS')
ctyc <- ctyc[-25,]
pvalues <- c(pvalues, wilcox.test(thetayc~match, data=ctyc, paired=T)$p.value)

dtyc <- subset(tyc, match == 'LS_RS' | match == 'LB_RB')
dtyc <- dtyc[-25,]
pvalues <- c(pvalues, wilcox.test(thetayc~match, data=dtyc, paired=T)$p.value)

etyc <- subset(tyc, match == 'LS_RS' | match == 'LB_LS')
etyc <- etyc[-25,]
pvalues <- c(pvalues, wilcox.test(thetayc~match, data=etyc, paired=T)$p.value)

ftyc <- subset(tyc, match == 'LB_RB' | match == 'LB_LS')
pvalues <- c(pvalues, wilcox.test(thetayc~match, data=ftyc, paired=T)$p.value)

pvalues <- p.adjust(pvalues, method = "BH")

# now for exit comparisons

stoolpvalues <- c()

htyc <- subset(tyc, match=='RB_SS' | match=='RS_SS')
htyc <- htyc[-25,]
stoolpvalues <- c(stoolpvalues, wilcox.test(thetayc~match, data=htyc, paired=T)$p.value)

ityc <- subset(tyc, match=='RB_SS' | match=='LB_SS')
stoolpvalues <- c(stoolpvalues, wilcox.test(thetayc~match, data=ityc, paired=T)$p.value)

jtyc <- subset(tyc, match=='RB_SS' | match=='LS_SS')
stoolpvalues <- c(stoolpvalues, wilcox.test(thetayc~match, data=jtyc, paired=T)$p.value)

ktyc <- subset(tyc, match=='RS_SS' | match=='LB_SS')
ktyc <- ktyc[-25,]
stoolpvalues <- c(stoolpvalues, wilcox.test(thetayc~match, data=ktyc, paired=T)$p.value)

ltyc <- subset(tyc, match=='RS_SS' | match=='LS_SS')
ltyc <- ltyc[-25,]
stoolpvalues <- c(stoolpvalues, wilcox.test(thetayc~match, data=ltyc, paired=T)$p.value)

mtyc <- subset(tyc, match=='LB_SS' | match=='LS_SS')
stoolpvalues <- c(stoolpvalues, wilcox.test(thetayc~match, data=mtyc, paired=T)$p.value)

stoolpvalues <- p.adjust(stoolpvalues, method = "BH")

alltyc <- read.table("../data/process/allshared.summary", sep = '\t', header = T, row.names=NULL)
alltyc <- separate(alltyc, label, into= c('pt1', 'samp1'), sep="-", remove=F)
alltyc <- separate(alltyc, comparison, into= c('pt2', 'samp2'), sep="-", remove=F)
alltyc <- alltyc[-1]
alltyc <- alltyc[-7]

#ultimately want a plot of all points where pt1 == pt2 in one bar and all of the others in another column 
#unite and make column of 0/1 for matches? then can plot 1 and 0s 
#should i separate out lumen and mucosa ? sure or no not for now

alltyc["same_pt"] <- NA

for (i in 1:nrow(alltyc)){
  if (alltyc$pt1[i] == alltyc$pt2[i]){
    alltyc$same_pt[i] <- 1
  }
  else alltyc$same_pt[i] <- 0
}

alltyc[10] <- as.factor(alltyc[10])

inter_medians <- aggregate(thetayc ~ same_pt, alltyc, median)
```
